descriptive anaysis

### 2020-06-06 src/bbData2020.Rmd
further updates to explore temporal features

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE}
#add column for day of the week
bb2020$weekday <- wday(bb2020$date, label = TRUE)
#create 2 dataframes for 2 matching periods
Wks2019 <- selectByDate(bb2020, start = "2019-01-21", end = "2019-06-02")
names(Wks2019)[1:2] <- c("dateOnly", "date")
Wks2020 <- selectByDate(bb2020, start = "2020-01-20", end = "2020-05-31")
names(Wks2020)[1:2] <- c("dateOnly", "date")
#timeplots
TimeVar2019 <- timeVariation(Wks2019, pollutant = "speeddown", statistic = "mean")
TimeVar2019up <- timeVariation(Wks2019, pollutant = "speedup", statistic = "mean")
TimeVar2020 <- timeVariation(Wks2020, pollutant = "speeddown", statistic = "mean")
TimeVar2020up <- timeVariation(Wks2020, pollutant = "speedup", statistic = "mean")
timePlot(Wks2019, pollutant = "speeddown", avg.time = "day", smooth = TRUE)
timePlot(Wks2020, pollutant = "speeddown", avg.time = "day", smooth = TRUE)
timePlot(Wks2019, pollutant = "speedup", avg.time = "day", smooth = TRUE)
timePlot(Wks2020, pollutant = "speedup", avg.time = "day", smooth = TRUE)
```

@@

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE}
DateCount19 <- count(Wks2019, dateOnly)
names(DateCount19) <- c("Date19", "tests19")
HrCount19 <- count(Wks2019, date, hour)
HrSpeed19 <- summarise(group_by(Wks2019, date, hour), mean(speeddown))
HrStats19 <- left_join(HrCount19, HrSpeed19)
names(HrStats19) <- c("Date19", "Hour19", "test19", "meanSp19")
DateCount20 <- count(Wks2020, dateOnly)
names(DateCount20) <- c("Date20", "tests20")
HrCount20 <- count(Wks2020, date, hour)
HrSpeed20 <- summarise(group_by(Wks2020, date, hour), mean(speeddown))
HrStats20 <- left_join(HrCount20, HrSpeed20)
names(HrStats20) <- c("Date20", "Hour20", "test20", "meanSp20")
DateCount <- cbind(DateCount19, DateCount20)
HrStats <- cbind(HrStats19, HrStats20)  # I GET AN ERROR HERE
write.csv(DateCount, "DailyTestFreq.csv")
write.csv(HrStats, "HrTestFreqMean.csv")
Plot2019 <- ggplot(DateCount19, aes(Date19, tests19))
Plot2019 + geom_line()
Plot2020 <- ggplot(DateCount20, aes(Date20, tests20))
Plot2020 + geom_line()
```

>>>>

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE}
#add column for day of the week
bb2020$weekday <- wday(bb2020$date, label = TRUE)
#create 2 dataframes for 2 matching periods
Wks2019 <- selectByDate(bb2020, start = "2019-01-21", end = "2019-06-02")
names(Wks2019)[1:2] <- c("dateOnly", "date") #413788 obs
Wks2020 <- selectByDate(bb2020, start = "2020-01-20", end = "2020-05-31")
names(Wks2020)[1:2] <- c("dateOnly", "date") #521773 obs
#timeplots
TimeVar2019 <- timeVariation(Wks2019, pollutant = "speeddown", statistic = "mean", name.pol = "speedown 2019")
TimeVar2019up <- timeVariation(Wks2019, pollutant = "speedup", statistic = "mean", name.pol = "speedup 2019")
TimeVar2020 <- timeVariation(Wks2020, pollutant = "speeddown", statistic = "mean", name.pol = "speeddown 2020")
TimeVar2020up <- timeVariation(Wks2020, pollutant = "speedup", statistic = "mean", name.pol = "speedup 2020")
timePlot(Wks2019, pollutant = "speeddown", avg.time = "day", smooth = TRUE, name.pol = "speeddown 2019")
timePlot(Wks2020, pollutant = "speeddown", avg.time = "day", smooth = TRUE, name.pol = "speeddown 2020")
timePlot(Wks2019, pollutant = "speedup", avg.time = "day", smooth = TRUE, name.pol = "speedup 2019")
timePlot(Wks2020, pollutant = "speedup", avg.time = "day", smooth = TRUE, name.pol = "speedup 2020")
```

@@

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE}
DateCount19 <- count(Wks2019, dateOnly)
names(DateCount19) <- c("Date19", "tests19")
HrCount19 <- count(Wks2019, dateOnly, hour)
HrSpeed19 <- summarise(group_by(Wks2019, dateOnly, hour), mean(speeddown))
HrSpeed19up <- summarise(group_by(Wks2019, dateOnly, hour), mean(speedup))
HrStats19 <- left_join(HrCount19, HrSpeed19)
HrStats19 <- left_join(HrStats19, HrSpeed19up)
names(HrStats19) <- c("dateOnly", "hour", "test19", "meanSp19", "meanSp19up")
DateCount20 <- count(Wks2020, dateOnly)
names(DateCount20) <- c("Date20", "tests20")
HrCount20 <- count(Wks2020, dateOnly, hour)
HrSpeed20 <- summarise(group_by(Wks2020, dateOnly, hour), mean(speeddown))
HrSpeed20up <- summarise(group_by(Wks2020, dateOnly, hour), mean(speedup))
HrStats20 <- left_join(HrCount20, HrSpeed20)
HrStats20 <- left_join(HrStats20, HrSpeed20up)
names(HrStats20) <- c("dateOnly", "hour", "test20", "meanSp20", "meanSp20up")
DateCount <- cbind(DateCount19, DateCount20)
HrStats <- cbind(HrStats19, HrStats20)
#add columns tests per hour, mean speeddown per hr, mean speed up per hr
Wks2019 <- left_join(Wks2019, HrStats19, by = c("dateOnly", "hour"))
Wks2020 <- left_join(Wks2020, HrStats20, by = c("dateOnly", "hour"))
#frequency plot
timePlot(Wks2019, pollutant = "test19", avg.time = "hour", smooth = TRUE, name.pol = "hourlyTests 2019")
timePlot(Wks2020, pollutant = "tests20", avg.time = "hour", smooth = TRUE, name.pol = "hourlyTests 2020")
TimeVar2019n <- timeVariation(Wks2019, pollutant = "test19", statistic = "mean", name.pol = "hourlytests 2019")
TimeVar2020n <- timeVariation(Wks2020, pollutant = "test20", statistic = "mean", name.pol = "hourlytests 2020")
Plot2019 <- ggplot(DateCount19, aes(Date19, tests19))
Plot2019 + geom_line()
Plot2020 <- ggplot(DateCount20, aes(Date20, tests20))
Plot2020 + geom_line()
